\documentclass[a4paper,10pt]{article}

\usepackage[left=0.55in,right=0.55in,top=0.6in,bottom=0.6in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}

\pagestyle{empty}
\setlength{\tabcolsep}{0in}
\linespread{0.88}

\setlist[itemize]{itemsep=0pt, topsep=2pt, leftmargin=*}

\titlespacing*{\section}{0pt}{6pt}{4pt}
\titleformat{\section}
  {\scshape\raggedright\normalsize}
  {}{0em}{}[\titlerule]

\begin{document}

%-------------------- HEADING --------------------
\begin{center}
    {\LARGE \scshape Smera Rawal} \\
    Chennai, India \\
    \href{mailto:smerarawal@gmail.com}{smerarawal@gmail.com} $|$ 
    \href{https://www.linkedin.com/in/smera-rawal}{LinkedIn}
\end{center}

%-------------------- EDUCATION --------------------
\section{Education}

\textbf{Vellore Institute of Technology, Chennai}  (Pursuing) \hfill 2024 -- 2028 \\
B.Tech in Computer Science and Data Science \\
Relevant Coursework: Operating Systems, DBMS, OOPs, Data Structures, Computer Networks

%-------------------- TECHNICAL SKILLS --------------------
\section{Technical Skills}

\textbf{Languages:} Python, C, C++, Java \\
\textbf{Web:} HTML, CSS, JavaScript \\
\textbf{Machine Learning \& Deep Learning:} Supervised \& Unsupervised Learning, Feature Engineering, LSTM, CNN, Transformers, Neural Networks, GenAI, Reinforcement Learning, NLP \\
\textbf{Libraries/Frameworks:} NumPy, Pandas, Matplotlib, Scikit-learn, TensorFlow, Keras \\
\textbf{Tools:} Git, Linux, VS Code

%-------------------- RESEARCH --------------------
\section{Research and Experience}

\noindent\textbf{Learning Stellar Differential Rotation and Spot Evolution from Photometric Time Series (Ongoing)}
\begin{itemize}
    \item Investigating differential rotation and starspot evolution from photometric light curves using deep sequence modeling.
    \item Rotational modulation and spot migration via LSTM, 1D CNN and Transformers for long temporal dependencies.
    \item Applying Lomb--Scargle periodogram for irregular time-series frequency extraction and frequency-domain splitting.
    \item Designing sliding-window temporal representations and evaluating robustness under synthetic noise injection.
    \item Interpreting learned latent representations to study astrophysical rotational dynamics and variability patterns.
\end{itemize}
\noindent\textbf{Quantitative Finance Research Consultant at WorldQuant}
\begin{itemize}
    \item Developed multiple alpha signals based on market microstructure and statistical patterns in financial time-series
    \item Achieved Maximum Sharpe Ratio of 2.66, returns of over 24 while maintaining a drawdown less than 5%.
    \item Applied statistical validation techniques including Sharpe ratio, IC and turnover analysis
\end{itemize}
\noindent\textbf{Data Analytics Intern, Unessa Foundation} 
\begin{itemize}
    \item Analyzed and processed datasets to extract actionable insights supporting organizational initiatives.
    \item Performed data cleaning, visualization, and reporting to improve decision-making efficiency.
\end{itemize}

%-------------------- PROJECTS --------------------
\section{Projects}

\noindent\textbf{Astronomical Light Curve Classification using LSTM vs MLP vs 1D CNN}
\begin{itemize}
    \item Built an end-to-end stellar time-series pipeline with preprocessing, normalization and synthetic variability modeling.
    \item Implemented and compared LSTM, MLP and 1D CNN architectures for star classification performance benchmarking.
    \item Analyzed temporal dependency capture using multiple sliding-window configurations and feature scaling strategies.
    \item Injected synthetic Gaussian noise and conducted hyperparameter tuning to evaluate robustness.
\end{itemize}

\noindent\textbf{ML-Based Drug Repurposing Pipeline (GNN + LLMs)}
\begin{itemize}
    \item Built an end-to-end pipeline combining GNN-based binding affinity prediction with Tanimoto similarity on ChEMBL
    \item Modeled molecules as graphs using RDKit and trained a GIN network to predict pChEMBL values
    \item Integrated LangChain for biomedical knowledge extraction and interpretable reasoning of drug--target interactions
    \item Generated ranked repurposing candidates with explainable scoring and visualization
\end{itemize}


\noindent\textbf{Visual Financial Intelligence System (ViT + RAG)}
\begin{itemize}
    \item Multimodal financial analysis pipeline using Vision Transformer (ViT) to extract patterns from stock chart images.
    \item Retrieval-Augmented Generation (RAG) system using FAISS for semantic retrieval of financial knowledge.
    \item Interpretable trading insights using large language models (LLMs), improving explainability of technical analysis.
\end{itemize}

%-------------------- LEADERSHIP --------------------
\section{Leadership \& Activities}

\noindent\textbf{Logistics Lead, TEDx VITC}
\begin{itemize}
    \item Managed event logistics, vendor coordination and cross-functional execution for large-scale campus events.
\end{itemize}

\noindent\textbf{Management and Outreach Member, Google Developer's Group}
\begin{itemize}
    \item Organized technical events, workshops and external collaborations to foster developer engagement.
\end{itemize}

\noindent\textbf{Sponsorships and Outreach Member, Enactus and Business Innovation Community}
\begin{itemize}
    \item Contributed to ideation sessions, startup case discussions and innovation-driven problem solving initiatives.
\end{itemize}
\textbf{Content Writer, Sahayatha Club} 
\begin{itemize}
    \item Created engaging and informative content for social initiatives, increasing outreach and audience engagement.
\end{itemize}
%-------------------- CERTIFICATIONS --------------------
\section{Certifications}

     WorldQuant Gold - IQC 2026, Generative AI Certification - IBM, Machine Learning, Stanford University (Andrew Ng)


%-------------------- RESEARCH INTERESTS --------------------
\section{Relevant Academic Interests}

Scientific Machine Learning, Time-Series Modeling, Stellar Variability Analysis, Representation Learning, Robust Deep Sequence Models

\end{document}
